Automated Software Engineering Final Paper (Working Title)

### 2015-12-13 paper/paper.tex
Added Arisholm paper to related work

Bird et al \cite{Bird} examined whether development that is largely distributed produces more failures than development that is mainly collocated. The belief at the time was that distributed development was prone to more failures than collocated development. They found a negligible difference in both code metrics and failures between the two methods of development. The authors examined how the developers working on Windows Vista managed to work well together among teams located in different countries based on the relationships between the development sites, cultural barriers, communication, consistent use of tools, end to end ownership, common schedules, and organizational integration. They recommended that companies wishing to distribute development across sites located far apart to employ similar strategies to overcome some of the difficulties associated with such an endeavor.

>>>>

Bird et al \cite{Bird} examined whether development that is largely distributed produces more failures than development that is mainly collocated. The belief at the time was that global development was prone to more failures than collocated development. They found a negligible difference in both code metrics and failures between the two methods of development. The authors examined how the developers working on Windows Vista managed to work well together among teams located in different countries based on the relationships between the development sites, cultural barriers, communication, consistent use of tools, end to end ownership, common schedules, and organizational integration. They recommended that companies wishing to distribute development across sites located far apart to employ similar strategies to overcome some of the difficulties associated with such an endeavor.

Arisholm et al \cite{Arisholm} examined different ways to build and evaluate fault prediction models. First, they tested a variety of modeling techniques, such as neural networks, C4.5 with some variants, support vector machines, and logistic regression. They then looked at different metrics:  Process measures, OO code measures, and delta measures. Finally, they looked at ROC area and cost-effectiveness as evaluation criteria. They found that the choice of modeling technique did not have much of an impact when evaluated with both criteria tested. Among the metric sets, they found that process measures provide a significant improvement over the others, even though they are typically more costly to collect.  They also suggested cost-effectiveness as a good evaluation technique instead of traditional techniques like precision and recall as smarter decisions can be made to prioritize which parts of the project are tested and bug-fixed.
